Article Title

### 2014-10-30 manuscript.tex
removed plos.tex and plos.pdf, updated manuscript.tex

To demonstrate that estimator rankings did not depend on the assumption of gaussianity, we repeated the cross-validated evaluation with a non-Gaussian data generating model, non-Gaussian loss function, or both:

First, we replaced the data-generating model with the pairwise Ising model \cite{Hertz:2011}, which has equivalent mathematical form to the MVN model,
\begin{equation}
    x\sim \frac 1 {Z(S,h)} \exp\left(-\frac 1 2 x^\T S x + h^\T x \right),
\end{equation}
but defined on the binary domain $x\in\{-1,+1\}^p$ rather than the continuous domain of the MVN model. The partition function $Z(S,h)$ normalizes the distribution on the models' respective domains. 
For the MVN, the matrix $S$ is the precision matrix or the inverse of the covariance matrix; and the mean values are $\mu=-S^{-1}h$.  In the Ising model, $-S$ is the matrix of pairwise interactions and $h$ is the vector of intrinsic activity drives of individual cells but $S$ and $h$ do not have a closed-form relationship to the mean activity and the covariance matrix of the distribution. 
However, both distributions have the same structure of pairwise conditional dependencies: zeros in the matrix $S$ indicate conditional independence between the corresponding pair of neurons.

First, replacing the normal loss function with the quadratic loss function, 
\begin{equation}\label{eq:quad}
\loss{C,C_{\sf sample}^\prime}=\frac 1 {p^2}\Tr(C^{-1}C_{\sf sample}^\prime-I)^2
\end{equation}
did not affect estimator rankings (Fig.~S1 A--D).

@@

The same evaluation based on the quadratic loss function,
instead of the normal loss function reproduced the same relationship between the estimators (Fig.~S3).

This suggests that the results of this study are robust to the choice of the loss function and do not depend on the assumption of gaussianity.

@@

We evaluated the covariance matrix estimators a loss function based on multivariate normal log likelihood.  However, this does not limit the applicability of its conclusions to normal distributions. Indeed our major findings could be reproduced using other loss functions (compare Fig.~\ref{fig:3} and Fig.~S3).  Other probabilistic models, fitted to the same data, could also serve as estimators of the covariance matrix.  If a different model yields better estimation of the covariance matrix than the estimator proposed here, we believe that its structure should deserve consideration as the better representation of the functional connectivity.

@@

\newpage
\section*{Supporting Information Legends}
%
% Please enter your Supporting Information captions below in the following format:
%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
% 
\begin{description}
\item {\bf Figure S2. Optimization of hyperparameters of the $C_{\sf sparse+latent}$ estimator.} {\bf A.} Validation loss (Eq.~\ref{eq:full-loss}) for the example site in Fig.~\ref{fig:2} and \ref{fig:4} as a function of the hyperparameters $\alpha$ and $\beta$ of the $C_{\sf sparse+latent}$ estimator (Eq.~\ref{eq:c-sl} and Eq.~\ref{eq:ma}). In all panels, the red cross marks the optimal value found by the pattern search algorithm described in Methods.
{\bf B.} The connectivity ($1-\mbox{sparsity}$) of the sparse component $S$ as a function of $\alpha$ and $\beta$ for the example site.
{\bf C.} The number of latent units, \emph{i.e.}~the rank of the low-rank component $L$, as a function of hyperparameters $\alpha$ and $\beta$.
{\bf D.} The loss function as a function of the connectivity and the number of latent units.

\item {\bf Figure S3. Performance of estimator $C_{\sf sparse+latent}$ with respect to \emph{quadratic loss} (Eq.~\ref{eq:quad}) relative to the other estimators: $C_{\sf sample}$, $C_{\sf diag}$, $C_{\sf factor}$, and $C_{\sf sparse}$.} All comparisons showed significant advantage of estimator $C_{\sf sparse+latent}$ ($p<10^{-3}$ in each comparison, Wilcoxon signed rank test, $n=27$ sites in 14 mice). 
\end{description}

\end{document}

>>>>

To demonstrate that estimator rankings did not depend on the assumption of gaussianity, we repeated the cross-validated evaluation with a non-Gaussian data-generating model, the pairwise Ising model (Fig.~S1).   The Ising model \cite{Hertz:2011} has equivalent mathematical form to the MVN model,
\begin{equation}
    x\sim \frac 1 {Z(S,h)} \exp\left(-\frac 1 2 x^\T S x + h^\T x \right),
\end{equation}
but is defined on the multivariate binary domain $x\in\{-1,+1\}^p$ rather than the continuous domain of the MVN model. 
The partition function $Z(S,h)$ normalizes the distribution on the models' respective domains. 
In the MVN model, the matrix $S$ is the precision matrix or the inverse of the covariance matrix; and the mean values are $\mu=-S^{-1}h$.  
For the Ising model, $-S$ is the matrix of pairwise interactions and $h$ is the vector of the cells' individual activity drives. In contrast to the MVN model,  $S$ and $h$ do not have a closed-form relationship to the mean firing rates or their covariance matrix. 
Both distributions have the same structure of pairwise conditional dependencies: zeros in the matrix $S$ indicate conditional independence between the corresponding pair of neurons.

@@

@@

We evaluated the covariance matrix estimators a loss function based on multivariate normal log likelihood.  However, this does not limit the applicability of its conclusions to normal distributions. Other probabilistic models, fitted to the same data, could also serve as estimators of the covariance matrix.  If a different model yields better estimation of the covariance matrix than the estimator proposed here, we believe that its structure should deserve consideration as the better representation of the functional connectivity.

@@

\newpage
\section*{Supporting Information Legends}
%
% Please enter your Supporting Information captions below in the following format:
%\item{\bf Figure SX. Enter mandatory title here.} Enter optional descriptive information here.
% 
\begin{description}
\item {\bf Figure S1. Performance of covariance estimators when the ground truth is the  Ising model.} 
{\bf A.} With the ground truth having a diagonal matrix of dependencies (no pairwise dependencies),

\item {\bf Figure S2. Optimization of hyperparameters of the $C_{\sf sparse+latent}$ estimator.} {\bf A.} Validation loss (Eq.~\ref{eq:full-loss}) for the example site in Fig.~\ref{fig:2} and \ref{fig:4} as a function of the hyperparameters $\alpha$ and $\beta$ of the $C_{\sf sparse+latent}$ estimator (Eq.~\ref{eq:c-sl} and Eq.~\ref{eq:ma}). In all panels, the red cross marks the optimal value found by the pattern search algorithm described in Methods.
{\bf B.} The connectivity ($1-\mbox{sparsity}$) of the sparse component $S$ as a function of $\alpha$ and $\beta$ for the example site.
{\bf C.} The number of latent units, \emph{i.e.}~the rank of the low-rank component $L$, as a function of hyperparameters $\alpha$ and $\beta$.
{\bf D.} The loss function as a function of the connectivity and the number of latent units.
\end{description}
\end{document}
